---
title: "rapidraker"
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  progress = FALSE,
  error = FALSE, 
  message = FALSE,
  warning = FALSE
)

options(digits = 2)
```

> A fast version of the Rapid Automatic Keyword Extraction (RAKE) algorithm

[![Linux Build Status](https://travis-ci.org/crew102/rapidraker.svg?branch=master)](https://travis-ci.org/crew102/rapidraker)
[![CRAN version](http://www.r-pkg.org/badges/version/rapidraker)](https://cran.r-project.org/package=rapidraker)

## Installation

You can get the stable version on CRAN:

```r
install.packages("rapidraker")
```

The development version of the package requires you to compile the latest Java source code in [rapidrake-java](https://github.com/crew102/rapidrake-java), so installing it is not as simple as making a call to  `devtools::install_github()`.

## What is `rapidraker`?

`rapidraker` is an R package that provides an implementation of the same keyword extraction algorihtm (RAKE) as `slowraker`. However, `rapidraker::rapidrake()` is written in Java, whereas `slowraker::slowrake()` is written in R. This means that you can expect `rapidrake()` to be considerably faster than `slowrake()`.

## Usage

`rapidrake()` has the same arguments as `slowrake()`, and both functions output the same type of object. You can therefore substitue `rapidrake()` for `slowraker()` without making any additional changes to your code. 

```{r, eval = FALSE}
library(slowraker)
library(rapidraker)

data("dog_pubs")
rakelist <- rapidrake(txt = dog_pubs$abstract[1:5])
```

```{r, eval = TRUE, results = 'hide', echo = FALSE}
# Note, we have to split the README.Rmd up like this so that it doesn't print 
# the progress bar.
library(slowraker)
library(rapidraker)
options(width = 100, digits = 2)

data("dog_pubs")
rakelist <- rapidrake(txt = dog_pubs$abstract[1:5])
```

`rapidrake()` outputs a list of data frames. Each data frame contains the keywords that were extracted for an element of `txt`:

```{r}
rakelist
```

You can bind these data frames together using `slowaker::rbind_rakelist()`:

```{r}
rakedf <- rbind_rakelist(rakelist, doc_id = dog_pubs$doi[1:5])
head(rakedf, 5)
```

## Learning more

* To learn more about the API used by both `slowraker` and `rapidraker`, head over to `slowraker`'s [webpage](https://crew102.github.io/slowraker/index.html).
